% Auto-generated List of Figures with references
\begin{singlespace}
\noindent \textbf{Fig.}\ref{fig:landau_zener_results} --- Coherence magnitude (a) and energy spectra comparison (b) showing meter-induced dephasing and energy rescaling.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:fidelity_contour} --- Fidelity maps vs anneal time $T$ and coupling $x_0$; contours of constant effective time $T(1+x_0)$.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:lz_scaling} --- Landau–Zener infidelity vs $T$ at different $x_0$, demonstrating collapse under $T\\to T(1+x_0)$.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:fidelity_diff} --- Fidelity change due to non-commuting meter dynamics ($\\omega\\neq0$) for LZ and 3-qubit Ising systems.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:optimal_ramp} --- Lowest two energy levels comparing locally optimal (gap-proportional) and linear annealing schedules (LZ and 3-qubit QA).\\[2pt]
\noindent \textbf{Fig.}\ref{fig:optimal_diff} --- Fidelity difference: optimal local adiabatic schedule vs linear schedule.\\[2pt]
\noindent \textbf{Fig.} \ref{fig:gap_profiles} --- Characteristic energy gap profiles for random Ising instances ($N=3,4,5$) with statistics.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:average_schedule} --- Performance of averaged optimal schedules vs linear and instance-optimal schedules.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:constrained_results} --- (a) TTS speedup ratio vs $N$ for full/constrained QND; (b) constrained protocol fidelity vs $x_0$.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:larger_isings_2b} --- Larger Ising fidelity-contour variants (2–4 qubits).\\[2pt]
\noindent \textbf{Fig.}\ref{fig:larger_isings_5_2b} --- 5-qubit larger-Ising fidelity-contour variant.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:larger_isings_4b} --- Larger Ising fidelity-difference variants (3–5 qubits).\\[2pt]
\noindent \textbf{Fig.}\ref{fig:larger_isings_6_7} --- Larger Ising results for 6–7 qubits.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:larger_systems_fidelity} --- Candidate plots (fidelity increase and mesh) for larger systems.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:optimal_ramp_average} --- Average annealing schedules compared to linear and instance-optimal schedules ($N=3$--$5$).\\[2pt]
\noindent \textbf{Fig.}\ref{fig:antiferromagnetic_results} --- Antiferromagnetic / mixed-coupling regime results and comparisons.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:NonCommutationRescaling} --- Effective energy rescaling under non-commuting meter dynamics.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:interference_analysis} --- Interference analysis: fidelity ripples, analytical interference factor, and overlay.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:COLD_fig1} --- COLD reproduction: two-spin annealing protocol fidelity comparisons.\\[2pt]
\noindent \textbf{Fig.}\ref{fig:COLD_fig2} --- COLD reproduction: five-spin system comparisons (BPO vs COLD).\\[2pt]
\end{singlespace}

% Note: page numbers assigned at compile-time. Include this file in the main document with \input{list_of_figures.tex}.
